The \dealii Library, Version 9.6

### 2024-09-20 9.6/paper.tex
Add founding support.

In the current release, we have put substantial work into this switch. The following omits the \texttt{LinearAlgebra} prefix for readability.
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
Most of the interfaces are usable at this point even if some functionality existing in the \texttt{TrilinosWrappers} classes
is still missing, most noticably a wrapper for an algebraic-multigrid preconditioner.

@@

\todo[inline]{Sebastian: Anything to list here?}

>>>>

In the current release, we have put substantial work into this switch,
as outlined below. In the following list, we omit the common namespace
\texttt{LinearAlgebra::} prefix on all mentioned
\texttt{TpetraWrappers} symbols for readability:
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
Most of the interfaces are usable at this point even if some functionality existing in the \texttt{TrilinosWrappers} classes
is still missing, most noticably a wrapper for an algebraic-multigrid preconditioner.

@@

Sebastian Kinnewig is supported by the Deutsche Forschungsgemeinschaft (DFG) under Germany’s Excellence
Strategy within the Cluster of Excellence PhoenixD (EXC 2122, Project ID 390833453)
